Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-04-08 paper.tex
Tweaked tables

This manuscript uses an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}. The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software. The schematic for the model used here is presented be seen in Figure \ref{fig:schematic}.
}
The electrical interface model of \cite{Franks2005} {\color{red} (is this true, I can't see a faradaic part in Franks)} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch. While Scott and Single \cite{ScottSingle2013} incorporate memristors into their model, they has been omitted here for simplicity. {
    \color{blue}
    The memristors in \cite{ScottSingle2013} are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions. In an implanted setting an electrode should never be operated in a Faradaic counduction mode, and certainly never to the point of becoming diffusion limited. It is for this reason the memristors have been removed.
}

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $NaCl$ & $8.0\thinspace g$ \\ \hline
            $KCl$ & $0.2\thinspace g$ \\ \hline
            $Na_{2}HPO_{4}$ & $1.44\thinspace g$ \\ \hline
            $KH_{2}PO_{4}$ & $0.24\thinspace g$ \\ \hline
            Distilled Water & $1.0$\thinspace L \\ \hline
        \end{tabular}
    \end{center}
    \caption{PBS stock solution ingredients}
    \label{tab:PBSrecipe}
\end{table}

@@

The pH level of the stock was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.

It should be noted that the resistive mesh created in this step models only the resistivity of the solution bulk. This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes. We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
            $R_{sri}$ & $R_{eri}$ $3/4$ \\ \hline
            $R_{li}$ & 3.71 / $\sigma$ \\ \hline
            Depth & 5 layers \\ \hline
            Padding & 3 layers \\ \hline
        \end{tabular}
    \end{center}
    \caption{Resistor mesh parameters. $\sigma$ measured in units of $S/cm$}
    \label{tab:RESparams}
\end{table}

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $m$ & $1.34$ \\ \hline
            $k$ & $1.773$\\ \hline
            $|Z|\: @\: 1Hz$& $3284 \times concentration^{-0.158}$ \\ \hline
            $R_{S}$ & $13.38 \times concentration^{-0.8397} $\\ \hline
        \end{tabular}
    \end{center}
    \caption{Displacement parameter scaling}
    \label{tab:CPEparams}
\end{table}

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $i0$ & 2.757e-12\\ \hline
            $n$ & 1.36\\ \hline
        \end{tabular}
    \end{center}
    \caption{Faradaic parameters}
    \label{tab:FaradaicParams}
\end{table}

@@

    {\color{blue}
        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface. Whatever reaction occurs first in the relevant electrolyte is the reaction that diode aims to mimic. We observe that the current increases near exponentially around this point so we use a diode to mimic that. We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match where this occurs.

@@

    3. The parameters provided in Table II include reference to an unexplained term sigma (σ). I presume this is the conductivity of saline (correct symbol and units for conductivity). For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.

>>>>

This manuscript uses an adapted version of the compact non-linear model presented by Scott and Single \cite{ScottSingle2013}. The model is compact in that it is suitable for entering into SPICE, i.e., freely available electrical circuit simulation software. The schematic for the model used here is presented be seen in Figure \ref{fig:schematic}.
}
The electrical interface model of \cite{Franks2005} {\color{red} (is this true, I can't see a faradaic part in Franks)} and \cite{ScottSingle2013} has two parts, a displacement branch and a Faradaic branch.

Scott and Single \cite{ScottSingle2013} incorporate memristors into their model. {
    \color{blue}
    These memristors are used to mimic a diffusion limited current conduction mode, i.e., their purpose is to throttle electrical current associated with Faradaic reactions. In an implanted setting an electrode should never be operated in a Faradaic counduction mode and certainly never to the point of becoming diffusion limited; for this reason the memristors have been omitted.
}

@@

\begin{table}
    \caption{PBS stock solution ingredients}
    \label{tab:PBSrecipe}
    \begin{center}
        \begin{tabular}{r | l}
            Ingredient & Quantity \\
            \hline
            $NaCl$ & $8.0\thinspace g$ \\
            $KCl$ & $0.2\thinspace g$ \\
            $Na_{2}HPO_{4}$ & $1.44\thinspace g$ \\
            $KH_{2}PO_{4}$ & $0.24\thinspace g$ \\
            Distilled Water & $1.0$\thinspace L \\
        \end{tabular}
    \end{center}
\end{table}

@@

The pH level of the stock solution was measured, using a calibrated EDT Instruments BA-350 pH meter, to have a pH of 7.4. No pH adjustments were made to the derived solutions.

    In Table \ref{tab:RESparams}, $\sigma$ refers to the conductivity of the solution, measured in units of Siemens per centimeter. Solution conductivity was measured using an EDT instruments RE 388 TX Microprocessor Conductivity Meter.

    It should be noted that the resistive mesh created in this step models only the resistivity of the solution bulk. This means that no resistive contribution from the electrode/electrolyte interface is included in these measurements as voltage measurements are always across pairs of non-driven electrodes. We determine the fixed resistance of a single interface, $R_{S}$, when fitting parameters to the displacement component.
}

@@

\begin{table}
    \caption{Resistor mesh parameters.\\ Electrolyte conductivity ($\sigma$) is expressed in units of $S/cm$}
    \label{tab:RESparams}
    \begin{center}
        \begin{tabular}{r | l}
            Parameter & Value \\
            \hline
            $R_{eri}$ ($\Omega$)& 0.407/$\sigma\\
            $R_{sri}$ ($\Omega$)& $R_{eri}\times 3/4\\
            $R_{li}$ ($\Omega$)& 3.71 / $\sigma$ \\
            Depth (layers) & 5 \\
            Padding (layers) & 3 \\
        \end{tabular}
    \end{center}
\end{table}

\begin{table}
    \caption{Measured conductivity of PBS solutions. {\color{red} Should I add this?}}
    \label{tab:PBSconductivity}
    \begin{center}
        \begin{tabular}{r | l}
            Concentration (X-PBS) & Conductivity ($\mu S/cm$)\\
            \hline
            1.0 & $15800$ \\
            0.5 & $4360$\\
            0.25 & $1860$\\
            0.05 & $931$\\
            0.025 & $492$\\
        \end{tabular}
    \end{center}
\end{table}

@@

\begin{table}
    \caption{Displacement parameter scaling}
    \label{tab:CPEparams}
    \begin{center}
        \begin{tabular}{r | l}
            Parameter & Value \\
            \hline
            $m$ & $1.34$ \\
            $k$ & $1.773$\\
            $|Z|\: @\: 1Hz$ $(\Omega)$& $3284 \times concentration^{-0.158}$ \\
            $R_{S}$ $(\Omega)$& $13.38 \times concentration^{-0.8397} $\\
        \end{tabular}
    \end{center}
\end{table}

@@

\begin{table}
    \caption{Faradaic parameters}
    \label{tab:FaradaicParams}
    \begin{center}
        \begin{tabular}{r | l}
            Parameter & Value \\
            \hline
            $i0$ & $2.757\thinspace pA$\\
            $n$ & 1.36\\
        \end{tabular}
    \end{center}
\end{table}

@@

    {
        \color{blue}
        The diodes are there to model the change in current attributed to the first biologically damaging reaction that occurs at the electrode/electrolyte interface. Whatever reaction occurs first in the relevant electrolyte is the reaction that diode aims to mimic. We observe that the current increases near exponentially around this point so we use a diode to mimic that. We expect this reaction may not be the same in-vivo as it is in-vivo but the properties of a diode can be altered to match where this occurs.

@@

    3. The parameters provided in Table II include reference to an unexplained term sigma ($\sigma$). I presume this is the conductivity of saline (correct symbol and units for conductivity). For completeness, I recommend the authors explain this term, provide the numeric value (or values) that they used, provide how they adjusted this with concentration, and reference the source of their numeric data.
